### 2017-03-23 ThesisText/statistics.tex
Minor corrections on statistics

Table~\ref{tab:moodle_users_stats} shows some stats regarding Moodle users.
Some of the explored projects listed in the background, like~\TODO{cite}, have
a number of students around 800 to 900 which is greater then the number of
students in this dataset, but they also have a lower number of courses, for
example~\TODO{cite} has 7, where this dataset has 77.

@@

This leads to the conclusion not only that the levels of activity remain
relatively constant during the semester, but also leads to the conclusion that
many students don't quit the courses even i they fail.

@@

\TODO{Explain what are active courses and show the plot}

@@

@@

    \caption
        [Total Number of Activities vs Mean of Activities per Week]
        {Total Number of Activities vs Mean of Activities per Week.}

@@

@@

Table~\ref{tab:results_stats} shows some statistics on the results data.

@@

    \begin{tabular}{| l | r |}
        \hline
        Number of results           & 716 \\ \hline
        Number of non-empty results & 57  \\ \hline
        Number of approved students & 334 \\ \hline
    \end{tabular}

@@

\section{Profile}

\section{Moodle Logs}

>>>>

Table~\ref{tab:moodle_users_stats} shows some stats regarding Moodle users.
Some of the explored projects listed in the background, like~\cite{ind_001},
have a number of students around 800 to 900 which is greater then the number of
students in this dataset, but they also have a lower number of courses, for
example~\cite{ind_001} has 7, where this dataset has 77.

@@

This leads to the conclusion not only that the levels of activity remain
relatively constant during the semester, but also leads to the conclusion that
many students don't quit the courses even if they fail.

@@

@@

The concept of active course needs to be understood. A course is active from
week 0 until the last week for which there is any activity. For example, if the
last activity of a course is on week 20, then the course is active from week 0
until week 20.

Figure~\ref{fig:stat_006} shows a graphs bar with the number of active courses
per week, and again shows the total number of activities over these bars. We
see that the number of active courses fall correlates with the fall of the
total number of activities. This further reinforces the notion that the
activity of courses remains relatively the same as the semester moves forward.

@@

    \caption
        [Total number of activities vs mean of activities per week]
        {Total number of activities (Right) vs mean of activities per week
        (Left).}

@@

    \includegraphics[width=\linewidth]{../src/stat_006_results/plot}

    \caption
        [Total number of activities vs mean of activities per week]
        {Total number of activities (right) vs total active courses (Left).}

    \label{fig:stat_006}
\end{figure}

@@

Table~\ref{tab:results_stats} shows some statistics on the results data. We see
that from the available 716 entries, 334 of the, refer to instances of a
student getting approved on a course.

As seen in section~\ref{sec:results}, the dataset containing the results has
the fields \textit{Grade}, \textit{Results}, and \textit{FinalResult} for a
combination of course and student. However, some objects have no values for
those three fields. When that happens, we interpret the objects as having the
student not getting approved on that course. From the 716 results, 57 of them
are empty.

@@

    \begin{tabular}{| l | r |}
        \hline
        Number of results           & 716 \\ \hline
        Number of non-empty results & 659  \\ \hline
        Number of approved students & 334 \\ \hline
    \end{tabular}

@@
